Gammapy: A Python package for gamma-ray astronomy

### 2023-03-22 src/ms-review.tex
Remove forward references in section 2.1
Signed-off-by: Régis Terrier <rterrier@apc.in2p3.fr>

\subsection{\gammapy data analysis workflow}
The first step in \gammaray data analysis is the selection and extraction of observations
based on their metadata including information such as pointing direction, observation
time and observation conditions. The access to the events data and instrument 
reponse per observation is supported by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.

The next step of the analysis is the data reduction, where all observation events and instrument
responses are filled into or projected onto a common physical coordinate system, defined by
a map geometry. The definition of the map geometry typically consists of a spectral dimension
defined by a binned energy axis and of spatial dimensions, which either define 
a spherical projection from celestial coordinates to a pixelised image space
or a single region on the sky. The \code{gammapy.maps} subpackage provides
general multidimensional geometry objects and the associated data structures
(see Section~\ref{ssec:gammapy-maps}).

%% CN: I would actually distingusih two cases here:
%% 1) the Bkg is already provided as a parametrisation
%% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
After all data have been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
these models can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the FoV background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the FoV or energy boundaries of the instrument are typically
associated with a systematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 \enquote{safe} data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).

%% CN: for 1D analysis datasets, DL4 can actually be written as OGIP files,
%% so as reduced datasets in a general format, not specific to Gammapy.
%% Maybe you can briefly mention that this is due to the fact that the 1D Poisson
%% spectral analysis is liong consilidated, but this also means that Gammapy 's
%% dataset can handle lower energy data, e.g. X-ray.
%% We also said in the abstract that Gammapy is compliant with other specifications
%% adopted in high-energy astrophysics.
The counts data and the reduced IRFs in the form of maps are bundled into datasets
that represent the fourth data level (DL4). These reduced datasets can be written to disk,
in a format specific to \gammapy to allow users to read them back at any time later
for modelling and fitting. Different variations of such datasets support different 
analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
fit, allowing one to combine different measurements, e.g. from different observations
but also from different instruments or event classes. They can also be used for binned
simulation as well as event sampling to simulate DL3 events data.
The various DL4 objects and the associated functionalities are
implemented in the \code{gammapy.datasets} subpackage (see Section~\ref{ssec:gammapy-datasets}).

The next step is then typically to model and fit the datasets, either
individually, or in a joint likelihood analysis. For this purpose \gammapy
provides a uniform interface to multiple fitting backends. In addition to
providing a variety of built-in models, including spectral,
spatial and temporal model classes to describe the \gammaray emission in the sky,
custom user-defined models are also supported.
Spectral models can be simple analytical models or more complex ones from radiation
mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
Independently or subsequently to the global modelling, the data can be
re-grouped to compute flux points, light curves and flux maps as well as significance
maps in different energy bands.
The modelling and fitting functionalities are implemented in the \code{gammapy.modeling},
\code{gammapy.estimators} and \code{gammapy.stats} subpackages (see respectively
Section~\ref{ssec:gammapy-modeling}, \ref{ssec:gammapy-estimators} and \ref{ssec:gammapy-stats}).

>>>>

\subsection{\gammapy data analysis workflow}
The first step in \gammaray data analysis is the selection and extraction of observations
based on their metadata including information such as pointing direction, observation
time and observation conditions.

The next step of the analysis is the data reduction, where all observation events and instrument
responses are filled into or projected onto a common physical coordinate system, defined by
a map geometry. The definition of the map geometry typically consists of a spectral dimension
defined by a binned energy axis and of spatial dimensions, which either define 
a spherical projection from celestial coordinates to a pixelised image space
or a single region on the sky.

%% CN: I would actually distingusih two cases here:
%% 1) the Bkg is already provided as a parametrisation
%% 2) the Bkg is not provided and, thus, has to be estimated from the obs.
After all data have been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
these models can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the FoV background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the FoV or energy boundaries of the instrument are typically
associated with a systematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 \enquote{safe} data in the spatial as well as energy dimension.

%% CN: for 1D analysis datasets, DL4 can actually be written as OGIP files,
%% so as reduced datasets in a general format, not specific to Gammapy.
%% Maybe you can briefly mention that this is due to the fact that the 1D Poisson
%% spectral analysis is liong consilidated, but this also means that Gammapy 's
%% dataset can handle lower energy data, e.g. X-ray.
%% We also said in the abstract that Gammapy is compliant with other specifications
%% adopted in high-energy astrophysics.
The counts data and the reduced IRFs in the form of maps are bundled into datasets
that represent the fourth data level (DL4). These reduced datasets can be written to disk,
in a format specific to \gammapy to allow users to read them back at any time later
for modelling and fitting. Different variations of such datasets support different 
analysis methods and fit statistics. The datasets can be used to perform a joint-likelihood
fit, allowing one to combine different measurements, e.g. from different observations
but also from different instruments or event classes. They can also be used for binned
simulation as well as event sampling to simulate DL3 events data.

The next step is then typically to model and fit the datasets, either
individually, or in a joint likelihood analysis. For this purpose \gammapy
provides a uniform interface to multiple fitting backends. In addition to
providing a variety of built-in models, including spectral,
spatial and temporal model classes to describe the \gammaray emission in the sky,
custom user-defined models are also supported.
Spectral models can be simple analytical models or more complex ones from radiation
mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
Independently or subsequently to the global modelling, the data can be
re-grouped to compute flux points, light curves and flux maps as well as significance
maps in different energy bands.
